The association of smoking status with SARS-CoV-2 infection, hospitalisation and mortality from COVID-19: A living rapid evidence review with Bayesian meta-analyses (`r paste(current_version)`)

### 2021-06-11 reports/manuscript.Rmd
checked manuscript

---
title: 'Smoking and COVID Living Review (`r paste(current_version)`): a bayesian analysis'
author: "David Simons, Lion Shahab, Jamie Brown and Olga Perski"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output:
  word_document:
    toc: yes
  html_document:
    highlight: zenburn
    toc: yes
    toc_float: yes
    number_sections: no
    theme: simplex
    css: C:/Users/ucbtds4/R Repositories/smoking_covid_bayes/css/style.css
    keep_md: no
editor_options:
  chunk_output_type: inline
bibliography: manuscript.bib
csl: harvard.csl
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,
                      warning = F,
                      message = F)
options(width = 180)
unlink('reports/markdown_report_cache', recursive = TRUE)
```

@@

#### [*Table 1.* All studies included in narrative review and meta-analysis]{#table-1}
``` {r table_1, include=T}
library(flextable)
library(ftExtra)
library(tidyverse)

@@

####    [*Table 2* SARS-CoV-2 infection by smoking status]{#table-2}
``` {r table_2, include=T}
readRDS(file = here::here("reports", "tables", "table_2.rds"))
```

@@

####    [*Table 3* COVID-19 hospitalsation by smoking status]{#table-3}
``` {r table_3, include=T}
readRDS(file = here::here("reports", "tables", "table_3.rds"))
```

@@

####    [*Table 4* COVID-19 disease severity by smoking status]{#table-4}
``` {r table_4, include=T}
readRDS(file = here::here("reports", "tables", "table_4.rds"))
```

@@

####    [*Table 5* COVID-19 attributed mortality by smoking status]{#table-5}
``` {r table_5, include=T}
readRDS(file = here::here("reports", "tables", "table_5.rds"))
```

@@

This living rapid review found uncertainty in the majority of `r paste(current_total)` studies arising from the recording of smoking status. Notwithstanding this uncertainty, compared with overall adult national prevalence estimates, recorded current smoking rates in most studies were lower than expected. In a subset of good and fair quality studies (n = `r paste(nrow(good_quality_2)+nrow(fair_quality_2))`), current but not former smokers had a reduced risk of testing positive for SARS-CoV-2 but current smokers appeared somewhat more likely to present for testing and/or receive a test. Data for current smokers on the risk of hospitalisation, disease severity and mortality were inconclusive, and favoured there being no important associations with hospitalisation and mortality and a small but important increase in the risk of severe disease. Former smokers were at increased risk of hospitalisation, disease severity and mortality compared with never smokers.

>>>>

---
title: 'The association of smoking status with SARS-CoV-2 infection, hospitalisation and mortality from COVID-19: A living rapid evidence review with Bayesian meta-analyses (`r paste(current_version)`)'
author: "David Simons, Lion Shahab, Jamie Brown and Olga Perski"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output:
  word_document:
    toc: yes
  html_document:
    highlight: zenburn
    toc: yes
    toc_float: yes
    number_sections: no
    theme: simplex
    css: C:/Users/ucbtds4/R_Repositories/smoking_covid_bayes/css/style.css
    keep_md: no
editor_options:
  chunk_output_type: inline
bibliography: manuscript.bib
csl: apa.csl
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,
                      warning = F,
                      message = F)
options(width = 180)
unlink('reports/markdown_report_cache', recursive = TRUE)
```

@@

#### [*Table 1.* All studies included in narrative review and meta-analysis]{#table-1}

``` {r table_1, include=T}
library(flextable)
library(ftExtra)
library(tidyverse)

@@

####    [*Table 2* SARS-CoV-2 infection by smoking status]{#table-2}

``` {r table_2, include=T}
readRDS(file = here::here("reports", "tables", "table_2.rds"))
```

@@

####    [*Table 3* COVID-19 hospitalsation by smoking status]{#table-3}

``` {r table_3, include=T}
readRDS(file = here::here("reports", "tables", "table_3.rds"))
```

@@

####    [*Table 4* COVID-19 disease severity by smoking status]{#table-4}

``` {r table_4, include=T}
readRDS(file = here::here("reports", "tables", "table_4.rds"))
```

@@

####    [*Table 5* COVID-19 attributed mortality by smoking status]{#table-5}

``` {r table_5, include=T}
readRDS(file = here::here("reports", "tables", "table_5.rds"))
```

@@

This living rapid review found uncertainty in the majority of `r paste(current_total)` studies arising from the recording of smoking status. Notwithstanding this uncertainty, compared with overall adult national prevalence estimates, recorded current smoking rates in most studies were lower than expected. In a subset of good and fair quality studies (n = `r paste(nrow(good_quality_2)+nrow(fair_quality_2))`), current but not former smokers had a reduced risk of testing positive for SARS-CoV-2 but current smokers appeared somewhat more likely to present for testing and/or receive a test. Data for current smokers on the risk of hospitalisation, disease severity and mortality were inconclusive, and favoured there being no important associations with hospitalisation and mortality and a small but important increase in the risk of severe disease. However, it should be noted that pooled estimates for the risk of hospitalisation and mortality in current smokers have numerically increased since the previous version (v10). Former smokers were at increased risk of hospitalisation, disease severity and mortality compared with never smokers.
